### 2016-04-23 manuscript-body.tex
add conclusion; change title of paper

Again, what's noteworthy is that rather than treating students'
non-canonical views as a burden for instruction, Bonar and Soloway
instead see them as an opportunity for programming language designers to
make languages better. Indeed, an empirical approach to language design has recently been articulated in Stefik and Siebert's work regarding language syntax's effect on novices. \cite{}

@@

>>>>

Again, what's noteworthy is that rather than treating students'
non-canonical views as a burden for instruction, Bonar and Soloway
instead see them as an opportunity for programming language designers to
make languages better. Indeed, an empirical approach to language design has recently been articulated in Stefik and Siebert's work regarding language syntax's effect on novices. \cite{stefik_intuitive_2011}

@@

In conclusion, we hold that Erin's reasoning---and that of other sense-makers---should count as valid ways of \texttt{knowing} in computing education and computing education research and should be attended to in computing learning environments. Modeling cognition only or primarily as a set of privileged, canonical knowledge is done at the expense of other productive knowledge and ways of knowing that students have.
